%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Freeman Curriculum Vitae
% XeLaTeX Template
% Version 3.0 (September 3, 2021)
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Authors:
% Vel (vel@LaTeXTemplates.com)
% Alessandro Plasmati
%
% License:
% CC BY-NC-SA 4.0 (https://creativecommons.org/licenses/by-nc-sa/4.0/)
%
%!TEX program = xelatex
% NOTE: this template must be compiled with XeLaTeX rather than PDFLaTeX
% due to the custom fonts used. The line above should ensure this happens
% automatically, but if it doesn't, your LaTeX editor should have a simple toggle
% to switch to using XeLaTeX.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
	10pt, % Default font size, can be between 8pt and 12pt
]{freemancv}

\columnratio{0.50, 0.50}

% Headers and footers can be added with the following commands: \lhead{}, \rhead{}, \lfoot{} and \rfoot{}
% Example right footer:
%\rfoot{\textcolor{headings}{\sffamily Last update: \today. Typeset with Xe\LaTeX}}

%----------------------------------------------------------------------------------------

\begin{document}

\begin{paracol}{2} % begin 2-col mode

\parbox[][0.11\textheight][c]{\linewidth}{ % Box to hold your name and CV title; change the fixed height as needed to match the colored box to the right
	\centering % Horizontally center text

	{\sffamily\Huge Louis Feuvrier} % Your name

	\medskip % Vertical whitespace

	{\textcolor{headings}{Computer Scientist}}

	\medskip % Vertical whitespace

	{\textit{« We do these things not because they are easy, but because we thought they were going to be easy. »}}

	\vfill % Push content to the top of the box
}

\section{Software philosophy}
After 20 years of deep interest in computers, I am most passionate about the
principles that go into architecting, developing and maintaining software. A
systems thinker at heart, I believe in doing so sustainably with a pure and
minimalist approach using a mix of modern (for devexp/ci) and less-modern
(for prod) technologies. I can make maintainable software a reality for lean
teams by ruthlessly removing complexity irrelevant to their domain.

\section{Tooling preferences}
\begin{supertabular}{r l} % Start a table with two columns, the table will ensure everything is aligned
	\tableentry{Loved}{linux, nixos, rust, mysql}{spaceafter}
	\tableentry{Proficent}{go, python, c}{spaceafter}
	\tableentry{Open to}{anything else (no java)}{spaceafter}
\end{supertabular}

\section{Extra curricular}
\begin{supertabular}{r l} % Start a table with two columns, the table will ensure everything is aligned
	\tableentry{ongoing/infra}
		{multi-host perso infra defined as a nix expr}{}
	\tableentry{\href{https://github.com/mqnfred/dustr}{2020/dustr}}
		{dart-rust compat layer/framework poc}{}
	\tableentry{\href{https://github.com/mqnfred/atof}{2020/atof}}
		{prototype of mumble implem in async rust}{}
	\tableentry{\href{https://github.com/mqnfred/hips}{2019/hips}}
		{rust cli/lib to store secrets alongside code}{}
	\tableentry{\href{https://github.com/mqnfred/clishe}{2019/clishe}}
		{a thin cli/shell builder framework for rust}{}
	\tableentry{2015/stm32f4}
		{arm bootloader for the stm32f4 board}{}
	\tableentry{2014/stos}
		{lab kernel, vfs/devfs/build/tasks/sched/...}{}
	\tableentry{2013/mammos}
		{homemade baremetal x86 early boot/os}{}
	\tableentry{2012/mips vm}
		{runs most mips programs}{}
	\tableentry{2012/42sh}
		{bash-like posix shell}{}
\end{supertabular}

\section{Education}
\begin{supertabular}{r l} % Start a table with two columns, the table will ensure everything is aligned
	\qualificationentry
		{2010 -- 2016} % Duration
		{Masters} % Degree
		{} % Honors, achievements or distinctions (e.g. first class honors)
		{Computer Science} % Department
		{EPITA, Paris, FR} % Institution
	\qualificationentry
		{2012} % Duration
		{Masters} % Degree
		{} % Honors, achievements or distinctions (e.g. first class honors)
		{Mathematics \& Computer Science} % Department
		{Tampere University of Technology, FI} % Institution
\end{supertabular}

\section{Workshops}
\textbf{Feuvrier L.} C programming support \textit{EPITA 2015}

\textbf{Feuvrier L.} Kernels: memory/interrupts/peripherals \textit{EPITA 2014}

\textbf{Feuvrier L.} Web security: csrf/xss/ssl/https/mim \textit{EPITECH 2014}

\section{Talks}
\textbf{Feuvrier L.}
\href{https://prezi.com/weom7ix5it3r/to-loot-you-first-need-to-boot/}
{To loot your first need to boot}
\textit{LSE internal 2014}

\textbf{Feuvrier L.}, Goncalves F.
\href{https://lse.epita.fr/data/lt/2015-10-13/lt-2015-10-13-Louis_Feuvrier_Fabien_Goncalves-tasks_in_stos.pdf}
{Early task management and userland threads in a toy kernel}
\textit{LSE Lightning talks 2015}
\medskip

\section{Articles}
\textbf{Feuvrier L.}
\href{https://blog.lse.epita.fr//2014/10/01/uefi-boot-stub-in-linux.html}
{UEFI boot stub in Linux}
\textit{LSE blog 2014}

\switchcolumn % switch to the right column
% colored details box
\parbox[top][0.11\textheight][c]{\linewidth}{ % Box to hold the colored box; change the fixed height as needed to match the box to the left
	\colorbox{shade}{ % Create colored box and specify background color
		\begin{supertabular}{@{\hspace{3pt}} p{0.05\linewidth} | p{0.775\linewidth}} % Start a table with two columns, the table will ensure everything is aligned
			\raisebox{-1pt}{\faPhone} & +1 (650) 495-4732 \\ % Phone number
			\raisebox{-1pt}{\faHome} & 252 Carl St, San Francisco, CA 94117 \\ % Address
			\raisebox{-1pt}{\small\faDesktop} & \href{https://louis.feuvrier.org}{https://louis.feuvrier.org} \\ % Website
			\raisebox{-1pt}{\small\faEnvelope} & \href{mailto:louis@feuvrier.org}{louis@feuvrier.org} \\ % Email address
			%\raisebox{-1pt}{\small\faDesktop} & \href{https://github.com/mqnfred}{https://www.LaTeXTemplates.com} \\ % 
			%\raisebox{-1pt}{\faLinkedinSquare} & \href{https://www.linkedin.com/in/username}{https://www.linkedin.com/in/username} \\ % LinkedIn profile
			% See fontawesome.pdf in the Fonts folder for all icons you can use
		\end{supertabular}
	}
	\vfill % Push content to the top of the box
}

\section{Work Experience}
\jobentry
	{Jun2018 -- Present} % Date(s)
	{San Francisco, CA} % Location
	{Uber Technologies Inc} % Organization/Location
	{Senior Software Engineer} % Job title
	{
		Part of technical leadership in storage platform. We support a
		large-scale, low-latency NoSQL store (petabytes of data at
		millions of qps in sub ms p50). Currently, my role ranges from
		coordination and mentorship to high-level design and reviews,
		development, operations and oncall management.
	}

\jobentry
	{Jan2017 -- May2018} % Date(s)
	{Aarhus, DK} % Location
	{Uber Technologies Inc.} % Organization
	{Software Engineer} % Job title
	{
		Designed/implemented/evolved SLI monitoring solutions (used by
		more than 40 teams at Uber nowadays) and the backup scheduling
		system for all of storage platform's offerings (schemaless,
		mysql, cassandra, ..) at Uber.
	}

\jobentry
	{Apr2016 -- Oct2016} % Date(s)
	{San Francisco, CA} % Location
	{Uber Technologies Inc.} % Organization
	{Intern} % Job title
	{
		Designed and implemented a state-machine based host/fleet
		lifecycle management for streaming platform's large fleet of
		kafka brokers.
	}

\jobentry
	{Oct2014 -- Feb2015} % Date(s)
	{San Francisco, CA} % Location
	{Arista Networks} % Organization
	{Intern} % Job title
	{
		Worked on the kernel team, maintaining the company's large
		patch set and tuning linux's rtnetlink network configuration
		capabilities to account for the switches' custom needs. Also
		dabbled in namespaces and virtual filesystems.
	}

\jobentry
	{Jan2014 -- Mar2016} % Date(s)
	{Paris, FR} % Location
	{EPITA Systems/security lab (LSE)} % Organization
	{Student Researcher/Teaching Assistant} % Job title
	{
		Implementation of VFS and devfs capabilities in the
		laboratory's research kernel. Contributed to early task
		management and many scheduler fixes. Taught kernel and web
		security courses, C programming help.
	}

\jobentry
	{Sep 2013 -- Jan 2014} % Date(s)
	{Paris, FR} % Location
	{Infinit} % Organization
	{Intern} % Job title
	{
		Ported the GUI client to linux platform, rewrote and sanitized
		the team's proprietary C++ SSL socket library.
	}

\section{Communication}
\begin{supertabular}{r l} % Start a table with two columns, the table will ensure everything is aligned
	\tableentry{native}{french}{}
	\tableentry{bilingual}{english}{}
	\tableentry{bilingual}{spanish}{}
\end{supertabular}
\end{paracol} % end 2-col mode
\end{document}
